---
title: "Job opportunities"
author: Robert ten Hove
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    css: corp-styles.css
    df_print: paged
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
version: '0.1'
---

Search trends in Google 

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
rm(list = ls())  # remove all data from global environment.
library(gtrendsR)
library(reshape2)
library(ggplot2)
library(scales)
```
Keywords
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
  
google.trends = gtrends(c("job opportunities"), gprop = "web", time = "all")[[1]]
google.trends = dcast(google.trends, date ~ keyword + geo, value.var = "hits")
rownames(google.trends) = google.trends$date
google.trends$date = NULL


```
Set timezone
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
Sys.setenv(TZ = "UTC")
```

Geographical region and time-frame for "job" 
Country(&region) abbreviations:
https://en.wikipedia.org/wiki/ISO_3166-2 

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google_job <- gtrends(c("job"), geo = c("NL", "DE", "ES", "FR", "US"), gprop = "web", time = "2019-10-01 2020-04-20")[[1]]

```
Plot trend of "job" from Google in four different countries. If hit is high, it means high google-search-popularity!

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}

google_job$date <- as.Date(google_job$date)

ggplot(google_job, aes(date, log(hits), colour = geo)) + 
  geom_point(size = 0.5) +
  geom_smooth(model = lm) + 
  xlab("Date") + 
  ylab("log 'Relative Interest'") + 
  ggtitle("Google trend on keyword 'job' in different countries") +
 # scale_x_date(labels = date_format("%m-%Y")) +
  scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") +
  theme_grey(base_size = 8)
```

Geographical region and time-frame for "animal sex"
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google.trends <- gtrends(c("animal sex"), geo = c("PK", "SA", "DE", "NL"), gprop = "web", time = "2010-01-01 2019-01-01")[[1]]

```
Search popularity in Germany(GE), Netherlands (NL), Pakistan (PK) and Saudi (SA) on "animal sex".

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
ggplot(google.trends, aes(date, hits, colour = geo)) + 
  geom_point()
```

...oh no.

Geographical region and time-frame for "mildew"
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google.trends <- gtrends(c("mildew"), geo = c("NL", "GB", "DE", "PL"), gprop = "web", time = "2010-01-01 2019-01-01")[[1]]

```
Search popularity in Germany(GE), Netherlands (NL), United Kingdom (GB) and Poland (PL) on "Mildew".
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
ggplot(google.trends, aes(date, hits, colour = geo)) + 
  geom_point()
```

Geographical region and time-frame for "mildew"
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google.trends <- gtrends(c("mildew"), geo = c("GB-ENG", "GB-NIR", "GB-SCT", "GB-WLS"), gprop = "web", time = "2010-01-01 2019-01-01")[[1]]

```
Search popularity in England (GB-ENG), Northern Ireland (GB-NIR), Scotland (GB-SCT) and Wales (GB-WLS) on "Mildew".
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
ggplot(google.trends, aes(date, hits, colour = geo)) + 
  geom_point()
```




