---
title: "Job opportunities"
author: Robert ten Hove
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    css: corp-styles.css
    df_print: paged
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
version: '0.1'
---

Search trends in Google 

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
rm(list = ls())  # remove all data from global environment.
library(gtrendsR)
library(reshape2)
library(ggplot2)
library(scales)
```
Keywords
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
  
google.trends = gtrends(c("job opportunities"), gprop = "web", time = "all")[[1]]
google.trends = dcast(google.trends, date ~ keyword + geo, value.var = "hits")
rownames(google.trends) = google.trends$date
google.trends$date = NULL


```
Set timezone
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
Sys.setenv(TZ = "UTC")
```

Geographical region and time-frame for "job" 
Country(&region) abbreviations:
https://en.wikipedia.org/wiki/ISO_3166-2 

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google_job <- gtrends(c("job"), geo = c("NL", "DE", "ES", "FR", "US"), gprop = "web", time = "2019-10-01 2020-04-20")[[1]]

```
Plot trend of "job" from Google in four different countries. If hit is high, it means high google-search-popularity!

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}

google_job$date <- as.Date(google_job$date)

p1 <- ggplot(google_job, aes(date, log(hits), colour = geo)) + 
       geom_point(size = 0.5) +
       geom_smooth(model = lm) + 
       xlab("Date") + 
       ylab("log 'Relative Interest'") + 
       ggtitle("Google trend on keyword 'job' in different countries") +
       # scale_x_date(labels = date_format("%m-%Y")) +
       scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") +
       theme_grey(base_size = 12)

p1

```

Geographical region and time-frame for **corona**.  
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google_covid <- gtrends(c("corona"), geo = c("NL", "DE", "ES", "FR", "US"), gprop = "web", time = "2020-01-01 2020-04-21")[[1]]

```
Search popularity on **Corona**.  

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}


hits_num <- function(x) {
    x$hits <- gsub("<1", NA, x$hits)
      x$hits <- as.numeric(x$hits)
        return(x)
}

google_covid <- hits_num(google_covid)


google_covid$date <- as.Date(google_covid$date)

p2<- ggplot(google_covid, aes(date, hits, colour = geo)) + 
      geom_point(size = 0.5) +
      geom_smooth(model = lm) + 
      xlab("Date") + 
      ylab("Relative Interest") + 
      ggtitle("Google trend on keyword 'corona' in different countries") +
      # scale_x_date(labels = date_format("%m-%Y")) +
      scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") +
      theme_grey(base_size = 12)

p2 

```


Geographical region and time-frame for **biology**.  
```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}
google_bio <- gtrends(c("biology"), geo = c("NL", "DE", "ES", "FR", "US"), gprop = "web", time = "2020-01-01 2020-04-21")[[1]]

```
Search popularity on **biology**.  

```{r echo=TRUE, warning=FALSE, message=FALSE,  include=TRUE}

# hits_num <- function(x) {
#     x$hits <- gsub("<1", NA, x$hits)
#       x$hits <- as.numeric(x$hits)
#         return(x)
# }
# 
# google_bio <- hits_num(google_bio)
# 

google_bio$date <- as.Date(google_bio$date)

p3<- ggplot(google_bio, aes(date, log(hits), colour = geo)) + 
      geom_point(size = 0.5) +
      geom_smooth(model = lm) + 
      xlab("Date") + 
      ylab("Relative Interest") + 
      ggtitle("Google trend on keyword 'biology' in different countries") +
      # scale_x_date(labels = date_format("%m-%Y")) +
      scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") +
      theme_grey(base_size = 8)

p3 

```